### 2019-09-10 README.Rmd
updated discussion points

- Graphics Group
    - email list
    - what should we do about gganimate/Halloween?
- LIME
    - I made a mistake when I told you that the full test dataset gets included in the ridge regression model (only the case of interest in included)

>>>>

- Graphics Group
    - what should we do about gganimate/Halloween?
    - treats?
- LIME
    - I made a mistake when I told you that the full test dataset gets included in the ridge regression model (only the case of interest in included)
    - Show updated journal on LIME (added a lot to document the package)
    - What did you think of my additions to section 2 of the paper?
    - New goal for 1st draft of paper: next Wednesday (9/18)
